Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-24 manuscript.Rmd
Implications Cultural Sociology II

Our results do not speak to exactly why intrapersonal change lacks significant explanatory power in understanding culture. First, it could be the case that adults are exposed to opportunities for change at the same rate, but become less willing to change. Or it could be that opportunities for durable change or the social conditions that facilitate durable change are just extremely uncommon. Changes in social structures, the life course, or cultural expectations could make intrapersonal change a much more consequential explanation for cultural differences.

Furthermore, the results we present related to education and political views suggest that the relative importance of different theoretical processes might differ by group. In line with life course perspectives, the results presented here suggest that importance of different experiences for cultural change are potentially contingent on previous experiences. For example, to the extent that we want to explain why people have different personal culture, the answer is likely different for people who have a college degree and those who do not. Mid-life experiences appear to have more significant implications for the personal culture for people without a college degree than for people with a college degree.

>>>>

Our analysis does not provide an answer as to why intrapersonal change seems to have limited impact on understanding cultural differences. The situations that promote durable change in personal culture might simply be rare. Alternatively, it is possible that adults do encounter opportunities, necessities, and incentives for change, but their ability or willingness to change decreases. All the more it is important to research when and how social situations can have encourage durable change in adults.

In this regard, our results regarding education and political views suggest that the significance of theoretical processes that can lead to such change can vary by group. Aligning with life course theories, it seems the importance [IMPACT ... ON ? IF IT'S NOT TOO CAUSAL] of experiences for cultural change may be contingent on other, prior experiences. For example, factors that shape personal cultural differences may likely differ for college and non-college graduates; the latter might be more profoundly influenced by mid-life experiences than the former in this regard. In trying to understand differences in personal culture, sociologists  should therefore pay more attention to the heterogeneous effects that different factors including social events, encounters, and situations can have. [NOT HAPPY WITH THIS LAST SENTENCE, BUT NEED SOME "MESSAGE". IF WE ARE TOO LONG, WE SHOULD LET GO OR EVEN COMPRESS THE LAST TWO PARAGRAPHS INTO ONE MUCH SHORTER ONE.]
